### 2018-06-06 IEEEtran/article.tex
forgot to update article

In this section, we will design a class diagram and a set of sequence diagrams that model the game of Nim. We will evaluate the difficulty of the design process. We will also evaluate the performance of simulation using the output theory and of verification of certain requirements using model expansion with respect to execution time and memory usage in terms of grounding size. For these metrics, we will use statistics reported by IDP itself.

@@

We simulated a game with two heaps. One of the heaps contains two objects and the other contains three objects. The first player removes all three objects from the second heap. The second player then removes one object from the first heap. Finally, the first player has no choice but to remove the last object and loses.
Figure \ref{fig:grounding} contains a graph of the size of the grounding reported by IDP per step. Figure \ref{fig:ms} shows a graph of the cumulative execution time per step measured in milliseconds. We can see that the grounding size was either one or three for most steps, with six exceptions. However, IDP was using a total of approximately 4.84 gigabyte of virtual memory at the final time step, which was also the greatest usage during this simulation run. The execution time graph shows a linear curve, indicating that the time interval between steps remained stable. It also shows that the total duration of the game was approximately 18 minutes, which is fairly long for a simple game like Nim.

@@

\begin{figure*}[!t]
	\centering
	\subfloat[Graph of grounding size per step]{\includegraphics[width=0.5\textwidth]{grounding}%
		\label{fig:grounding}}
	\hfil
	\subfloat[Graph of cumulative execution time per step]{\includegraphics[width=0.5\textwidth]{ms}}%
		\label{fig:ms}
	\caption{Graphs for grounding size and cumulative execution time}
	\label{fig:grounding-ms}
\end{figure*}

>>>>

In this section, we will design a class diagram and a set of sequence diagrams that model the game of Nim. We will evaluate the difficulty of the design process. We will also evaluate the performance of simulation using the output theory and of verification of certain requirements using model expansion with respect to execution time and memory usage in terms of virtual memory usage for the simulation and grounding size for the verifications.

@@

We simulated a game with two heaps. One of the heaps contains two objects and the other contains three objects. The first player removes all three objects from the second heap. The second player then removes one object from the first heap. Finally, the first player has no choice but to remove the last object and loses.
Table \ref{tab:sim-mem} contains the virtual memory usage at the start of each turn. It shows how simulating a game will require several gigabytes of memory.

Figure \ref{fig:boxplot} shows a boxplot of the execution time per time step, and figure \ref{fig:boxplot-nooutliers} shows a boxplot of the same data with the outliers removed. Half of the data lies between approximately 6.65 seconds and 6.9 seconds. Figure \ref{fig:boxplot-nooutliers} also shows the vast majority of the data is spread between approximately 6.5 seconds and 7.15 seconds. This distribution does lead to the total duration of the game being slightly less than 19 minutes, since the simulation was 116 steps long.

@@

\begin{table}[]
	\centering
	\begin{tabular}{|l|l|l|l|l|}
		\hline
		Turn 1 & 0,91 GB  \\ \hline
		Turn 2 & 2,09 GB  \\ \hline
		Turn 3 & 3,34 GB  \\ \hline
		End   & 4,84 GB  \\ \hline
	\end{tabular}
	\caption{Virtual memory usage during the simulation at the start of each turn}
	\label{tab:sim-mem}
\end{table}

\begin{figure*}[!t]
	\centering
	\subfloat[Boxplot of the execution time per simulation step]{\includegraphics[width=0.5\textwidth]{boxplot}%
		\label{fig:boxplot}}
	\hfil
	\subfloat[Boxplot of the execution time per simulation step with the outliers removed]{\includegraphics[width=0.5\textwidth]{boxplotnooutliers}}%
		\label{fig:boxplot-nooutliers}
	\caption{Boxplots for the execution time per simulation step}
	\label{fig:boxplots}
\end{figure*}

### 2018-06-06 chap-evaluatie/chap-evaluatie.tex
for june minor stuff
forgot to update article

Figuur \ref{fig:ms} bevat een boxplot van de rekentijd per simulatiestap, en figuur \ref{fig:ms-nooutliers} bevat een boxplot van dezelfde gegevens zonder de uitschieters. We zien dat voor ongeveer de helft van de tijdstappen de rekentijd ongeveer tussen 6,65 seconden en 6,9 seconden ligt. Globaal gezien is de rekentijd gespreid tussen ongeveer 6,5 seconden en 7,15 seconden. Dit zorgt er echter voor dat het ongeveer achttien minuten duurt om het spel volledig uit te spelen. Stap 23, 67 en 111 waren de stappen wanneer de speler een stapel kon kiezen. Het duurde ongeveer twee en een halve minuut om stap 23 te bereiken. Tussen stap 23 en 67 en tussen stap 67 en 111 was er telkens een tijdspanne van ongeveer vijf minuten.

>>>>

Figuur \ref{fig:ms} bevat een boxplot van de rekentijd per simulatiestap, en figuur \ref{fig:ms-nooutliers} bevat een boxplot van dezelfde gegevens zonder de uitschieters. We zien dat voor ongeveer de helft van de tijdstappen de rekentijd tussen ongeveer 6,65 seconden en 6,9 seconden ligt. Globaal gezien is de rekentijd gespreid tussen ongeveer 6,5 seconden en 7,15 seconden. Dit zorgt er echter voor dat het ongeveer negentien minuten duurt om het spel volledig uit te spelen, aangezien de simulatie in totaal 116 tijdstappen lang was. Stap 23, 67 en 111 waren de stappen wanneer de speler een stapel kon kiezen. Het duurde ongeveer twee en een halve minuut om stap 23 te bereiken. Tussen stap 23 en 67 en tussen stap 67 en 111 was er telkens een tijdspanne van ongeveer vijf minuten.
